Assembly Quality Metrics - Quast Results

### 2019-01-18 notebooks/assembly_metrics.Rmd
minor changes

# Plots

```{r}
ggplot(metrics2, aes(as.numeric(largest_contig), as.numeric(N50)))+
  geom_point()+
  geom_smooth(method = "lm")+
  theme_classic()+
  labs(x = "Largest contig size",
       y = "N50")

@@

```{r}
ggplot(metrics2, aes(as.numeric(no_of_contigs), as.numeric(N50)))+
  geom_point()+
  geom_smooth(method = "lm")+
  theme_classic()+
  labs(x = "Number of contigs",
       y = "N50")
```

>>>>

# Mean metrics
```{r}
print(paste0("Mean number of contigs: ", round(mean(metrics2$no_of_contigs), 1)))
print(paste0("Mean size of largest contigs: ", round(mean(metrics2$largest_contig), 1)))
print(paste0("Mean N50: ", round(mean(metrics2$N50), 1)))
print(paste0("Mean NG50: ", round(mean(as.numeric(metrics2$NG50)), 1)))

@@
